Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-09-12 README.Rmd
update readme

@@

## [🗎 PDF of draft 🗎](https://aaronpeikert.github.io/bayes-prereg/manuscript.pdf)

## [Slides for Talk](https://aaronpeikert.github.io/bayes-prereg/presentation.html)

>>>>

## [🗎 Manuscript draft 🗎](https://aaronpeikert.github.io/bayes-prereg/manuscript.pdf) / [Talk slides](https://aaronpeikert.github.io/bayes-prereg/presentation.html)

@@
